Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-10 paper/paper.tex
Finish off datasets section

@@

Despite the above limitations, we still use the original GoodNews dataset in
our experiments, along with the original train-validation-test split, to make
comparison to previous works easier. In the original split, the dataset was
randomly divided into...

\begin{table}[t]
	\caption {Summary of news captioning datasets}
	\label{tab:datasets}
	\centering
	\begin{tabular}{lll}
		\toprule
		  & GoodNews  &   NYTimes800k \\
		\midrule
      Number of articles & 257 033 & 445 828 \\
      Number of images   & 462 642 & 794 085 \\
      Average article length & 451 & 974 \\
      Average caption length & 18 & 18 \\
      Collection start month & Jan 10 & Mar 05\\
      Collection end month & Mar 18 & Sep 19 \\
      \midrule
      \% of words that are \\
      \quad -- nouns & 16\% & 16\% \\
      \quad -- pronouns & 1\% & 1\% \\
      \quad -- proper nouns & 23\% & 22\% \\
      \quad -- verbs & 9\% & 9\%  \\
      \quad -- adjectives & 4\% & 4\% \\
      \quad -- named entities & 27\% & 26\% \\
      \quad -- personal names & 9\% & 9\% \\
      \midrule
      \% of captions with \\
      \quad -- named entities & 97\% & 97\% \\
      \quad -- personal names & 68\% & 68\% \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{table}[t]
	\caption {NYTimes800k training, validation, and test splits}
	\label{tab:splits}
	\centering
	\begin{tabular}{llll}
		\toprule
		  & Training  &   Validation & Test \\
		\midrule
      Number of articles & &  \\
      Number of images   &  &  \\
      Start month &  & \\
      End month &  & \\
		\bottomrule
	\end{tabular}
\end{table}

In order to study how rare names are generated, we split the training,
validation, and test sets by time. The training set consists of 434K articles

\section{Model}

>>>>

\begin{table}[t]
	\caption {Summary of news captioning datasets}
	\label{tab:datasets}
	\centering
	\begin{tabular}{lll}
		\toprule
		  & GoodNews  &   NYTimes800k \\
		\midrule
      Number of articles & 257 033 & 445 819 \\
      Number of images   & 462 642 & 794 044 \\
      Average article length & 451 & 974 \\
      Average caption length & 18 & 18 \\
      Collection start month & Jan 10 & Mar 05\\
      Collection end month & Mar 18 & Sep 19 \\
      \midrule
      \% of words that are \\
      \quad -- nouns & 16\% & 16\% \\
      \quad -- pronouns & 1\% & 1\% \\
      \quad -- proper nouns & 23\% & 22\% \\
      \quad -- verbs & 9\% & 9\%  \\
      \quad -- adjectives & 4\% & 4\% \\
      \quad -- named entities & 27\% & 26\% \\
      \quad -- personal names & 9\% & 9\% \\
      \midrule
      \% of captions with \\
      \quad -- named entities & 97\% & 96\% \\
      \quad -- personal names & 68\% & 68\% \\
		\bottomrule
	\end{tabular}
\end{table}

@@

Despite the above limitations, we still use the original GoodNews dataset and
train-validation-test split in our experiments, in order to make comparison to
previous works easier. Using the original split, we have 421K training, 18K
validation, and 23K test captions. Given that the random split was done at the
caption level, it is possible for a training and test caption to share the same
article text.

@@

\begin{table}[t]
	\caption {NYTimes800k training, validation, and test splits}
	\label{tab:splits}
	\centering
	\begin{tabular}{llll}
		\toprule
		  & Training  &   Validation & Test \\
		\midrule
      Number of articles & 434 272 & 3 052 & 8 495 \\
      Number of images  & 764 049 & 7 852 & 22 143 \\
      Start month & Mar 15 & May 19 & Jun 19 \\
      End month & Apr 19 & May 19 & Aug 19 \\
		\bottomrule
	\end{tabular}
\end{table}

We split the training, validation, and test sets according to time, as shown in
Table \ref{tab:splits}. For example, the test set consists of all captions and
articles in the final three months of the collection period, from June to
August 2019. This has two advantages over the random split used in GoodNews.
Firstly, it prevents captions in the training and test sets from sharing the
same context article, thus making it better to see how well the model can
generalize. Secondly, due of the shift in the coverage of news over time, there
will be events and people in the test data that have never covered by the news
before. In particular, out of the 100K proper nouns in the test captions, 4\%
never appear in any training captions. Half of these also never appear in any
training article. Thus splitting by time allows us study how well the model can
generate rare names.

\section{Model Architectures}

\subsection{Context Inputs}

We propose a fully end-to-end model to generate news image captions. There
are three inputs to the model: the image, the faces, and article text. Using
ResNet-152, we obtain an embedding $X_I \in \mathbb{R}^{1024}$:
